Discovering governing reactions from concentration data

### 2017-11-02 docs/manuscript.tex
wip

	\section{Conclusion}
	In this work we have successfully applied and extended the SINDy method to not only parsimoniously detect potentially nonlinear terms in a dynamical system from possibly noisy data, but also yield, in this case, a sparse set of rates with respect to generating reactions (\ref{method:the-reactions}).

	In two examples it was demonstrated that, despite noisy data and unavailability of derivative measurements, a parsimonious generating reaction network that is qualitatively able to explain the observed data can be estimated. 
	In particular it was shown in the first example that if there is no ambiguity in the underlying model and ansatz reaction library, the actual rates can be recovered with decreasing time step, i.e., increasing resolution of the jump process. 
	In the second example we could obtain an even simpler model than what was used to generate data by making use of sparse regression and cross-validation.

>>>>

	\section{Conclusion}
	In this work we have successfully applied and extended the SINDy method to not only parsimoniously detect potentially nonlinear terms in a dynamical system from noisy data, but also yield, in this case, a sparse set of rates with respect to generating reactions (\ref{method:the-reactions}).

	In two examples it was demonstrated that despite noisy data and unavailable derivative measurements, a parsimonious generating reaction network that is qualitatively able to explain the observed data can be estimated. 
	In particular it was shown in the first example that if there is no ambiguity in the underlying model and ansatz reaction library, the actual rates can be recovered with decreasing time step, i.e., increasing resolution of the jump process. 
	In the second example we could obtain an even simpler model than what was used to generate data by making use of sparse regression and cross-validation.
